TCP Congestion Algorithms In Datacenters \\ \vspace{0.3cm} {\large LS Project}

### 2017-12-20 paper/paper.tex
paragraphs have a blank line in between instead of identation; removed unused appendix; changed "subsub:performing time-based automated tests"

@@

The tests will be performed using scripts written in Python [\ref{appendix:python}]. The scripts either act as controller or as disciple. The controller is responsible for controlling the tests, by synchronizing the time, exchanging commands to run, modify or stop the tests and gathering data. The disciple is the listener and executes all task commands the controller sends. The commands include getting the hostname of a disciple, setting the TCP congestion algorithm of a disciple, configuring the time of a disciple, starting the data transfer and measurement tools on the disciple and closing the connection with the controller.

@@

TODO Luc monitoring solution read up

@@

\appendix
\section{Python}
\label{appendix:python}
SCRIPT

>>>>

\setlength{\parindent}{0pt}
\setlength{\parskip}{\baselineskip}

@@

The tests will be performed using scripts written in Python\cite{git-lsproj}.
All nodes run a client, which performs actions as instructed by the controller.
The controller is responsible for controlling the tests: synchronizing time
among nodes, setting the TCP congestion algorithm of a node, and requesting one
node to open a listening port and instructing another to start sending at a
given time. Nodes report their measurements back to the controller.

@@

@@
